---
title: "Peng’s Exploratory Data Analysis Checklist"
output: html_document
date: "2024-03-04"
---

There are 10 steps in Peng's Exploratory Data Analysis Checklist. This worksheet will walk you through each step. 

## 1. FORMULATE YOUR QUESTION

Which states had the largest numbers of locations mapped in the GayGuides? 


## 2. READ IN YOUR DATA

```{r}
library(DigitalMethodsData)
data("gayguides")
```


## 3. CHECK THE PACKAGING

```{r}
nrow(gayguides)
ncol(gayguides)
```


## 4. RUN str()

```{r}
str(gayguides)
#making sure the numbers are "num"s and strings are "chr"s
```

## 5. LOOK AT THE TOP AND BOTTOM OF YOUR DATA

```{r}
head(gayguides)
```
```{r}
tail(gayguides)
```

## 6. CHECK YOUR "n"'S
```{r}
select(gayguides, state) %>% unique %>% nrow
```
```{r}
unique(gayguides$state)
#here we see that various abbreviations for DC, provinces, and Mexico inflate the number of states from 51 to 57. 
```

## 7. VALIDATE WITH ATLEAST ONE EXTERNAL SOURCE
```{r}
(gayguides[68, c(5, 8:9, 12:13)])
#Looking for the below lat and long
#32.79533055538653, -116.96098980394923
```

## 8. TRY THE EASY SOLUTION FIRST 
```{r}

```


## 9. CHALLENGE YOUR SOLUTION

## 10. FOLLOW UP












